---
title: "Assignment 2"
author: "Sarah Fondots"
date: "February 11, 2019"
output: html_document

---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8,echo = TRUE,warning = FALSE,message = FALSE)
options(digits = 4)
```
```{r}
library(ggplot2)
library(cowplot)
library(RCurl)
```

###Regression Analysis
This dataset of size n=51 are the 50 states and the District of Columbia in the United States from the year 2002.  The variables are:

* Birth rate per 1000 females 15-17 years old  
* Birth rate per 1000 females 18-19 years old  
* Violent crime rate per 100,000 citizens  
* Teen birth rate per 1000 births  
* Poverty rate (% of the state's population living in households with incomes below the federally defined poverty level)  

We will consider the poverty rate to be the predictor(x) for teen birth rate (y).

```{r}
data_url <- getURL("https://raw.githubusercontent.com/ActaeaPachypoda/STA319/master/Data/Poverty.csv")
Poverty <- read.csv(text = data_url)
```

1.First, create a scatterplot for teen birth rate vs. poverty rate.  Describe the relationship that is exhibited on the graph. Identify any outliers, possible curvature.  

```{r}
Poverty_Percent <- Poverty$PovPct
Teen_Birth <- Poverty$TeenBrth
povPlot <- ggplot(Poverty,aes(x=Poverty_Percent, y=Teen_Birth))+geom_point(size=2.5)
povPlot
```
This graph seems to have a positive linear relationship between poverty and teen birth rate.

2. Next, calculate the linear correlation coefficient.  Report the value of *r* under the graph.  

```{r}
r <- cor(Poverty_Percent,Teen_Birth)
povPlot
```
<center> *r* = `r r` </center>  
  
3. Finally, calculate the least squares model.  Assess the model for its usefulness in predicting and estimating teen birth rate using the poverty rate. To assess, use the values of R^2^ and CV.  

````{r}
rsqr <- summary(lm(Poverty_Percent~Teen_Birth, Poverty))$r.squared
CV <- NULL
```
<center> $R^2$ = `r rsqr` </center>
4. Estimate the teen birth rate when poverty rate is 12%.  Include a prediction interval for this value.  

```{r}
fit <- lm(Poverty_Percent~Teen_Birth, data = Poverty)
x <- .12
pRate <- fit$coefficients[1]+(fit$coefficients[2]*x)
```
Regression equation: Teen Birth Rate = `r fit$coefficients[1]` + `r fit$coefficients[2]` * Poverty Percent  

When the poverty rate is 12% we predict the teen birth rate will be: `r pRate`  

5. Create a scatterplot with prediction confidence bands around the regression line.  
```{r}
model <- lm(Teen_Birth~Poverty_Percent, data = Poverty)
pred.int <- predict(model, interval = "prediction")
myData <- cbind(Poverty, pred.int)

povPlot2 <- ggplot(myData,aes(x=Poverty_Percent,y=Teen_Birth))+geom_point(size=2.5)+stat_smooth(method = "lm")

povPlot2+geom_line(aes(y=lwr),color="red", linetype = "dashed")+geom_line(aes(y=upr), color = "red", linetype = "dashed")

```