---
title: "Assignment 3"
author: "Sarah Fondots"
date: "February 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8,echo = FALSE,warning = FALSE,message = FALSE)
```

```{r}
# Dataset and R settings
library(ggplot2)
library(cowplot)

setwd("E:/School/2019/Spring/319 - Applied Statistics/Data")
drillRock <- read.csv(file = "drillrock.csv",header = TRUE)
```

##Hydraulic Rock Drilling
Two processes for hydraulic drilling of rock are dry drilling and wet drilling.  In a dry hole, compressed air is forced down the drill rods to flush the cuttings and drive the hammer; in a wet hole water is forced down.  An experiment was conducted to determine whether the time *y* it takes to dry drill a distance of 5 feet in rock increases with depth *x* the results(extracted from *American Statistician*, February 1991) for one portion of the experiment are shown in the dataset.  

1. Generate the scatterplot of y (time to drill 5 ft) vs. x (depth at which drilling begins). Describe the graph, and the relationship between x and y. Include the calculated value of the linear correlation, $r$, under the graph.  

2. Conduct the complete simple linear regression analysis of the data. This will include the regression equation, a statement about $R^2$ and CV, and the t-test for non-zero slope.  

3. Predict time (y) for a depth of $x=300$ feet. Include confidence intervals for both the mean value of $y$ and the individual predicted value of $y$.  

4. What is the 95% confidence interval for the slope?  

5. Be sure to write up your analysis with complete sentences, grammar, and punctuation. Include all relevant Minitab output.  

### #1
```{r}
Drill_Time <- drillRock$time
Drill_Depth <- drillRock$depth

drillPlot <- ggplot(drillRock,aes(x=Drill_Depth, y=Drill_Time))+geom_point(size=2.5)+geom_smooth(method = "lm")
drillPlot
r <- cor(Drill_Depth,Drill_Time)
```
Value of linear correlation is $r$= `r r`  

### #2
```{r}
r2 <- r^2
fit <- lm(Drill_Time~Drill_Depth, data = drillRock)
tTest <- t.test(Drill_Depth,Drill_Time)
tStat <- tTest$statistic
pValue <- tTest$p.value
```
Regression equation: Drill Time = `r fit$coefficients[1]` + `r fit$coefficients[2]` * drill depth  
$r^2$: `r r2`  
CV:   
*t*-test for non-zero slope: `r tStat`  

### #3
```{r}
x <- 300
pTime <- fit$coefficients[1]+(fit$coefficients[2]*x) 
```
The predicted time it would take to drill 300 feet given our regression equation is `r pTime`.  

### #4
```{r}
interval <- confint(fit)

```
95% confidence interval for the slope: `r interval[2,1]` to `r interval[2,2]`