---
title: "Assignment 1"
author: "Sarah Fondots"
date: "February 6, 2019"
output: html_document
runtime: shiny
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8,echo = FALSE,warning = FALSE,message = FALSE)
options(digits = 4)
```
```{r}
library(RColorBrewer)
library(RCurl)

data_url <- getURL("https://raw.githubusercontent.com/ActaeaPachypoda/STA319/master/Data/WPOWER50.CSV")

wPower50 <- read.csv(text = data_url)  
```

###Problem 1
Generate a histogram of the variable Age.  Insert the graph here:  
```{r}
library(shiny)

age <- wPower50$AGE 
hist(age,col = brewer.pal(n=8, name = "Purples"))
```

###Problem 2
Describe the shape of the graph:  
This graph is skewed left

###Problem 3
Run the decriptive statistics on Age.  Insert the results from the session window and fill in the blanks below
```{r}
 n <- nrow(wPower50)
 sampleMean <-mean(age)
 sampleMedian <- median(age)
 sampleStandardDeviation <- sd(age)
 standardError <- sampleStandardDeviation/sqrt(n)
 minimum <- min(wPower50$AGE)
 maximum <- max(wPower50$AGE)
 coefficientOfVariation <- sampleStandardDeviation/sampleMean
```
|Table for Problem 3|
|------|-------|
| N |  `r n`|
|Sample Mean | `r sampleMean`|
|Sample Median | `r sampleMedian`|
|Sample Standard Deviation | `r sampleStandardDeviation`|
|Standard Error | `r standardError`|
|Minimum | `r minimum`|
|Maximum | `r maximum`|
|Cofficient of Variation | `r coefficientOfVariation`|

###Problem 4
```{r}
rangeMin <- sampleMean - (sampleStandardDeviation*2)
rangeMax <- sampleMean + (sampleStandardDeviation*2)
```
Range of $\bar{y} \pm 2s$ is `r rangeMin` to `r rangeMax`

###Problem 5
```{r}
percent <- sum(wPower50$AGE > rangeMin & wPower50$AGE < rangeMax)/n * 100
```
What proportion of the values in the dataset fall within the interval?
```{r}
proportion <- sum(wPower50$AGE >rangeMin & wPower50$AGE < rangeMax)
```
The proportion of the values in the dataset that fall within the specified interval is: `r proportion` out of `r n` or `r percent`%
