---
title: "Assignment 5"
author: "Sarah Fondots"
date: "April 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8,echo = FALSE,warning = FALSE,message = FALSE)
options(digits = 4)
```

```{r}
# Dataset and R settings
library(ggplot2)
library(knitr)
library(papeR)
library(Hmisc)
library(RCurl)

data_url <- getURL("https://raw.githubusercontent.com/ActaeaPachypoda/STA319/master/Data/flag2.csv")
flag2 <- read.csv(text = data_url)
```

# Multicollinearity

### Part 1  

Build the first-order model with y=contract, and include all independent variables, except DISTRICT. Copy and paste this model (and all subsequent models) into the table below, along with the other values.
```{r}
fit <- lm(flag2$PRICE ~ flag2$DOTEST + flag2$LBERATIO + flag2$STATUS + flag2$NUMBIDS + flag2$DAYSEST + flag2$RDLNGTH + flag2$PCTASPH + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTMOB + flag2$PCTSTRC + flag2$PCTTRAF + flag2$SUB, data = flag2)
summary(fit)
flagPlot <- ggplot(flag2,aes(x=flag2$DOTEST + flag2$LBERATIO + flag2$STATUS + flag2$NUMBIDS + flag2$DAYSEST + flag2$RDLNGTH + flag2$PCTASPH + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTMOB + flag2$PCTSTRC + flag2$PCTTRAF + flag2$SUB, y=flag2$PRICE))+ geom_point(size=2.5)+ stat_smooth(method = "lm",se=FALSE)
flagPlot
```
Model:
Price = `r fit$coefficients[1]` + `r fit$coefficients[2]`* DOTEST  + `r fit$coefficients[3]`* LBERATIO + `r fit$coefficients[4]`* STATUS + `r fit$coefficients[5]`* NUMBIDS + `r fit$coefficients[6]`* DAYSEST + `r fit$coefficients[7]`* RDLNGTH + `r fit$coefficients[8]`* PCTASPH + `r fit$coefficients[9]`* PCTBASE + `r fit$coefficients[10]`* PCTEXC + `r fit$coefficients[11]`* PCTMOB + `r fit$coefficients[12]`* PCTSTRC + `r fit$coefficients[13]`* PCTTRAF + `r fit$coefficients[14]`* SUB
### Part 2  

Examine model #1. Find variables that are highly correlated using pairwise correlations ( |r|>.8 indicates high correlation). Address the possible multicollinearity. Rerun the model.  
```{r}
corTable <- rcorr(as.matrix(flag2))
test <- corTable[["r"]]
tableOutput <- kable(test)

tableOutput

fit2 <- lm(flag2$PRICE ~ flag2$LBERATIO + flag2$STATUS + flag2$NUMBIDS + flag2$DAYSEST + flag2$RDLNGTH + flag2$PCTASPH + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTMOB + flag2$PCTSTRC + flag2$PCTTRAF + flag2$SUB, data = flag2)
summary(fit2)
flagPlot2 <- ggplot(flag2,aes(x=flag2$LBERATIO + flag2$STATUS + flag2$NUMBIDS + flag2$DAYSEST + flag2$RDLNGTH + flag2$PCTASPH + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTMOB + flag2$PCTSTRC + flag2$PCTTRAF + flag2$SUB, y=flag2$PRICE))+ geom_point(size=2.5)+ stat_smooth(method = "lm",se=FALSE)

flagPlot2
```
Price = `r fit2$coefficients[1]` + `r fit2$coefficients[2]`* LBERATIO + `r fit2$coefficients[3]`* STATUS + `r fit2$coefficients[4]`* NUMBIDS + `r fit2$coefficients[5]`* DAYSEST + `r fit2$coefficients[6]`* RDLNGTH + `r fit2$coefficients[7]`* PCTASPH + `r fit2$coefficients[8]`* PCTBASE + `r fit2$coefficients[9]`* PCTEXC + `r fit2$coefficients[10]`* PCTMOB + `r fit2$coefficients[11]`* PCTSTRC + `r fit2$coefficients[12]`* PCTTRAF + `r fit2$coefficients[13]`* SUB

### Part 3  

Examine model #2. Remove all nonsignificant terms at α=0.25. Rerun.  
```{r}
fit2 <- lm(flag2$PRICE ~ flag2$LBERATIO + flag2$STATUS + flag2$NUMBIDS + flag2$DAYSEST + flag2$RDLNGTH + flag2$PCTASPH + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTMOB + flag2$PCTSTRC + flag2$PCTTRAF + flag2$SUB, data = flag2)

lmSum <- summary(fit2)
pretty_lm <- prettify(lmSum)

fit3 <- lm(flag2$PRICE ~ flag2$NUMBIDS + flag2$DAYSEST + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTSTRC + flag2$SUB, data = flag2)
summary(fit3)
flagPlot3 <- ggplot(flag2,aes(x=flag2$NUMBIDS + flag2$DAYSEST + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTSTRC + flag2$SUB, y=flag2$PRICE))+ geom_point(size=2.5)+ stat_smooth(method = "lm",se=FALSE)
flagPlot3
```
Price = `r fit3$coefficients[1]` + `r fit3$coefficients[2]`* NUMBIDS + `r fit3$coefficients[3]`* DAYSEST + `r fit3$coefficients[4]`* PCTBASE + `r fit3$coefficients[5]`* PCTEXC + `r fit3$coefficients[6]`* PCTSTRC + `r fit3$coefficients[7]`* SUB

###Part 5
Examine model #4. Finally, remove nonsignificant interactions, and run the final model.  
```{r}
anova(fit3)
finalFit <- lm(flag2$PRICE ~ flag2$NUMBIDS + flag2$DAYSEST + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTSTRC, data = flag2)
summary(finalFit)

finalPlot <- ggplot(flag2,aes(x=flag2$NUMBIDS + flag2$DAYSEST + flag2$PCTBASE + flag2$PCTEXC + flag2$PCTSTRC, y=flag2$PRICE))+ geom_point(size=2.5)+ stat_smooth(method = "lm",se=FALSE)
finalPlot
```

Price = `r finalFit$coefficients[1]` + `r finalFit$coefficients[2]`* NUMBIDS + `r finalFit$coefficients[3]`* DAYSEST + `r finalFit$coefficients[4]`* PCTBASE + `r finalFit$coefficients[5]`* PCTEXC + `r finalFit$coefficients[6]`* PCTSTRC
